### 2014-07-31 Pero_Transcriptome.tex
pushing

The raw sequence reads were error corrected using the software bless \cite{Heo:2014cb}, using kmer=25, based on the developers recommendations. The error corrected adapter and quality trimmed following recommendations from MacManes \cite{MacManes:2014io} and Mbandi \cite{Christoffels:2014bg}. Specifically, adapter sequence contamination was removed, and low quality nucleotides (defined as \textsc{Phred} \textless 2) were removed using the program Trimmomatic version 0.32  \cite{Lohse:2012fg}. We concatenated sequence data from each reference tissue type and assembled them jointly using Trinity version released 17 July 2014 \cite{Haas:2013jq}. We used flags indicating the stranded nature of sequencing reads and set maximum allowable physical distance between read pairs to 999nt. The assembly was conducted on a lunix workstation with 64 cores and 512Gb RAM. To filter the raw sequence assembly, I estimated TPM for each assembled sequence using bwa-mem version 0.75 \cite{Li:2013wn} and eXpress version 1.51 \cite{Roberts:2012dh}, removing all contigs whose expression was less than TPM=1 \cite{Haas:2013jq}. The resulting assembly was characterized using the software package transrate (\url{https://github.com/Blahah/transrate})

\\

>>>>

The raw sequence reads were error corrected using the software bless \cite{Heo:2014cb}, using kmer=25, based on the developers recommendations. The error corrected adapter and quality trimmed following recommendations from MacManes \cite{MacManes:2014io} and Mbandi \cite{Christoffels:2014bg}. Specifically, adapter sequence contamination was removed, and low quality nucleotides (defined as \textsc{Phred} \textless 2) were removed using the program Trimmomatic version 0.32  \cite{Lohse:2012fg}. Reads from each tissue were assembled using Trinity version released 17 July 2014 \cite{Haas:2013jq}. We used flags indicating the stranded nature of sequencing reads and set maximum allowable physical distance between read pairs to 999nt. The assembly was conducted on a linux workstation with 64 cores and 512Gb RAM. To filter the raw sequence assembly, I downloaded \textit{Mus musculus} cDNA and ncRNA datasets from Ensembl (\url{ftp://ftp.ensembl.org/pub/release-75/fasta/mus_musculus/}), and the \textit{Peromyscus maniculatus} reference transcriptome from NCBI (\url{ftp://ftp.ncbi.nlm.nih.gov/genomes/Peromyscus_maniculatus_bairdii/RNA/}). I used a relaxed blastN procedure (evalue set to 10$^-10$) to identify contigs in the \textit{P. eremicus} dataset that are likely biological in origin. I then concatenated the filtered assemblies from each tissue into a single file, reducing redundancy using the software cd-hit-est \cite{Li:2006hr} using default setting except that only identical sequences were removed. The resulting assembly file was characterized using the software package transrate (\url{https://github.com/Blahah/transrate}). \\
